A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-05-29 Manuscript/vaught_2017.tex
updated paper May29th

\documentclass[twocolumn]{aastex6}
\usepackage{natbib}
\bibliographystyle{aasjournal}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught \altaffilmark{1}, Kate H. R. Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2},  Joseph Hennawi, J. Xavier Prochaska}

\altaffiltext{1}{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
 \altaffiltext{2}{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}

\begin{abstract}
Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. 
%
Presently, the mass and energy of these flows remain poorly constrained.
%
One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material. 
%
We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by \ion{Mg}{2} emission. 
%
Previous spectra of this sample have already revealed winds traced by \ion{Mg}{2} absorption. 
%
At our sample redshift, the \ion{Mg}{2} emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
%
The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which \ion{Mg}{2} is typically detected in absorption (i.e., projected distances $> 100$ kpc). 
%
Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to $z=1$. 
\end{abstract}

\maketitle

\section{Introduction}
Galactic scale outflows are considered to be a main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. 
%
%
In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. 
%
%
Even though outflows play a critical role in the star formation rates and mass of the host galaxy \citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
%
%
Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure \citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}. 
%
%
An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities.
%
%
Spectroscopy of galaxies from low to high redshifts and over a wide range of star formation rates have revealed outflows in galaxies which host large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012). 
%

% New Paragraph
One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations.
%
With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}. 
%
Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. 
%
It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2014}.

%%%% KHRR
\begin{itemize}
\item One novel way of developing these constraints is to trace the extent of winds in emission

\item This has been done in the optical (in H$\alpha$, [\ion{O}{3}]) for nearby starbursts -- these transitions trace a warm, shock-heated phase

\item In a study by \cite{Rubin_2011} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389. A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.

\item This latter mechanism makes it possible to study winds in emission beyond the local universe

\item Summary of experiment: in this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission in a sample of five distant ($z\sim0.7$) star-forming galaxies.  State the measurement we're making (SB limit, 2D absorption morphology).

\item Roadmap of paper sections for the reader.

\end{itemize}
%%%% end KHRR

@@

%%%% KHRR
\subsection{Sample Selection}

Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields \citep{Giavalisco2004} and the AEGIS survey field (the Extended Groth Strip; \cite{Davis2007}).  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7\arcmin \times 7\arcmin$ FORS2 pointing.

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions obtained from multiwavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.  These properties, as well as precise target coordinates, are listed in Table~\ref{tab:prop}.  \emph{HST}/ACS images of the galaxy sample are shown in 
Figure~\ref{fig.hstims}.  The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}.

%%%%

%
%The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.

\subsection{VLT/FORS2 Observations}
% New Paragraph
The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
%
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
%%%% KHRR
[{\bf This is demonstrated nicely in Figure~\ref{fig:spec_images}, so I think we should explain it fully and refer to it here.}]
%%%%

%
The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
%
Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
%
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
%%%% KHRR
[{\bf Explain seeing conditions here and refer to Figure~\ref{fig.seeing}.  You should also explain that the data were taken with three pointings offset by XXX arcmin somewhere in this subsection.}]
%%%%

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75,trim=50 100 100 350,clip=]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey \citep{Giavalisco2004}.
%From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.
Each image is $5\arcsec\times5\arcsec$.
%%% Reminder to KHRR: made with ~/Research/MgII/paper_mgii/Paper2/Analysis/figpro/vaught2017_make_justcolorims.pro
\label{fig.hstims}}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. 
%%%% KHRR
[{\bf Explain the two different y axes, add units to the left-hand y axis, explain what the vertical dashed lines mean.}]
%%%%
The \ion{Mg}{2} doublet falls fortuitously at the central wavelength of the HEII+47 filter. }
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
%%%% KHRR
\textbf{Top}: Seeing distribution for the XXX HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
\textbf{Bottom}: Same distribution for the XXX HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
%%%%
The seeing conditions were calculated by ESO and were provided in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

\subsection{Image Reduction}
The data were reduced using custom routines written in \textbf{Python}. 
%%
The images were first corrected by subtracting and removing the overscan region of the CCD. 
%%
Then the images were bias-subtracted and flat-fielded using twilight flats. 
%%
Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A. Cosmic algorithm.
%%
 The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.

%%
Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a root mean square (RMS) map of each science image.
%%
 These frames, in addition to the science images, are stacked to create a co-added RMS image.
%% New Paragraph
The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}.
%%
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
%%
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
%%
The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
%%
The images are median-combined in order to increase the signal-to-noise of any \ion{Mg}{2} emission. \textbf{SWarp} is also configured to produce RMS weight maps from our \textbf{SExtractor} weighted images.

%%%% KHRR
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.  
%Once image stacking was done, we were left with two images to perform photometry on. One image contains only continuum photons, while the other one contains continuum + \ion{Mg}{2} photons.  (see Figure \ref{fig:stacked_image}). 
%%%%
One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image. This is due to the imperfect overlap of the 3 pointings used. However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected. As a final step, both images are aligned in physical coordinates via the IRAF \textbf{Imalign} command \citep{Tody_1986}.

\begin{table}[h!]
\caption{VLT/FORS2 Observations: Filter and exposure properties of the VLT observations. The width of the transmission curves are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{images}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of ergs counts$^{-1}$ cm$^{-2}$ }\smallskip \\ 
& & & & & $\times10^{-17}$ \\ \hline 
HeII  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000 & 4722.46  & 44.82 & 38 &   36,937 & 2.40       \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\begin{table*}[t]
\centering
\caption{Properties of 5 galaxies in our sample :  These properties were taken from \cite{Rubin_2014}. All galaxies are at roughly the same redshift. The star formation rates for the sample range from 3.8 to 40.5 solar mass per year. The EW are for the blended components of the \ion{Mg}{2} doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra.  
%%%% KHRR
{\bf I think you have updates to these EWs and their errors, correct?}
%%%%
}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot} yr^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.00\pm 0.51$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$6.50 \pm 0.51$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$6.44 \pm 0.51$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$6.70 \pm 0.51$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$5.60 \pm 0.52$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}

\label{tab:prop}
\end{table*}

>>>>

\documentclass[twocolumn]{aastex61}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{amsmath}

\newcommand{\citeth}[1]{(\citeauthor{#1}\ \citeyear{#1})}
\newcommand{\citethnop}[1]{\citeauthor{#1}\ \citeyear{#1}}
\newcommand{\citethnopp}[1]{\citeauthor{#1}\ (\citeyear{#1})}

@@

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught}
\affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
\affiliation{Department of Physics, University of California, San Diego, CA}

 \author{Kate H. R. Rubin }
 \affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}

 \author{Fabrizio Arrigoni Battaia }
 \affiliation{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}

 \author{J. Xavier Prochaska}
 \affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}

\author{Joseph Hennawi,}
\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}

\correspondingauthor{Ryan Rickards Vaught}
\email{rjvaught@gmail.com}

\begin{abstract}

Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas from star-forming galaxies. Presently, the mass and energy of these flows remain poorly constrained. One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring this quantity via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe \ion{Mg}{2} to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$). We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, suggesting that the wind material does not extend beyond the galaxies' stellar component. Our observations also allow us to create the first ever spatially-resolved map of  \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.

\end{abstract}

\keywords{Galaxy Evolution, Galactic Winds}

\section{Introduction}\label{sec:intro}
Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physical mechanism that powers these galactic winds remains uncertain. Some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}). However it is very difficult to distinguish between these mechanisms with current observational techniques. Additionally, the impact galactic winds have on their host galaxies (i.e, their mass and energy content) has remained difficult to constrain with observations.

An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocities. Spectroscopy of galaxies from low to high redshifts probing cold gas which absorbs in \ion{Na}{1} and cool gas in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{Martin2012}; \citethnop{Rubin_2014}). Even though these probes can ascertain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.

One novel way of developing these constraints is to trace the extent of winds in emission. This has been demonstrated in the optical using rest frame near infrared transitions (i.e H$\alpha$ and \ion{O}{3} etc) as tracers for nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) because these transitions can trace the warm shock heated phase of the gas. However, it is difficult to use these rest frame near infrared transitions to probe winds at higher redshift because the faint emission can be redshifted into the infrared where the sky background is bright. At higher redshifts, it is advantageous to trace winds in the optical with the rest frame ultraviolet ion, \ion{Mg}{2} (Weiner et al. 2009; Kornei et al. 2013)\nocite{Weiner2009, Kornei2013}

Typically, studies of winds using \ion{Mg}{2} have focused on its absorption kinematics. However, recently in a study by \cite{Rubin_2011}, strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the 2D spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.  This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc. One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering.

In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy \citeth{Rubin_2011}. The photon scattering model, as explained, is described for the geometry of an isotropic wind \citeth{Prochaska_2011}. For anisotropic bi-conical winds, the emission induced from photon scattering will be highly suppressed. Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, further detections of extended \ion{Mg}{2} emission are by \cite{Erb2012} and \cite{Martin2013} have shown that emission is stronger for higher mass galaxies and that outflows can extend out to at least 18 kpc.

We aim to take advantage of this photon scattering as we present the first narrowband imaging of \ion{Mg}{2} line emission of 5 star-forming ($z \sim 0.7$) galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field. The value in using narrowband imaging is the ability to spatially resolve any absoroption and emission from a galaxy. We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is off-set from line filter. The continuum filter will allow us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet. With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}. Contrary to 1D spectra, the narrowband imaging has the ability to measure the surface brightness, optical depth and radial extent of a wind. This narrowband imaging will allow us to create the first ever spatially resolved map of \ion{Mg}{2} emission.

@@

\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al. 2014)\nocite{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004})and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.

The absorption line modeling presented in (Rubin et al. 2014)\nocite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates, taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.

\subsection{VLT/FORS2 Observations}
The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}). The transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.

FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$. Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters. Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing (see Figure \ref{fig.seeing}) ranged from 0.5 arcsec to 2.5 arcsec. The data were taken with three pointings offset by 0.25'.

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.73]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5'' $\times$ 5''.\label{fig:hstims}}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
\caption{KECK/LRIS spectrum of the sample galaxies and the transmission curves of the filters HeII+47 and HeII/3000+48. The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted the filter at each wavelength. Vertical dotted lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HEII+47 filter.}
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
\textbf{Top}: Seeing distribution for the 38 HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
\textbf{Bottom}: Same distribution for the 38 HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
The seeing conditions were calculated by ESO and were provided in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

\subsection{Image Reduction}
The data were reduced using custom routines written in \textbf{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A. Cosmic algorithm.
The astrometry solutions were calculated via Astrometry.net (Lang et al. 2010)\nocite{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \textbf{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
These frames, in addition to the science images, are stacked to create a co-added RMS image.

The final stacked images for each filter is obtained using \textbf{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015) \nocite{Battaia_2015}. 
The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are average-combined and weighted by the night-flat image in order to increase the signal-to-noise of any \ion{Mg}{2} emission. \textbf{SWarp} is also configured to produce RMS weight maps from our \textbf{SExtractor} weighted images. Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image. This is due to the imperfect overlap of the 3 pointings used. However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected.

\begin{table}[h!]
\caption{VLT/FORS2 Observations: Filter and exposure properties of the VLT observations. The width of the transmission curves are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{\text{img}}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline 
HeII  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000 & 4722.46  & 44.82 & 38 &   36,937 & 2.40       \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\begin{table*}[t]
\centering
\caption{Properties of 5 galaxies in our sample :  All galaxies are at roughly the same redshift. The star formation rates for the sample range from 3.8 to 40.5 solar mass per year. The EW include both components of the \ion{Mg}{2} doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra. \emph{HST}/ACS images of the galaxy sample are shown in Figure~\ref{fig:hstims}. The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}
\label{tab:prop}
\end{table*}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution (cite!) and each filter's transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al. (1990). We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives. Therefore we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{../Figures/HEII_final.png}
\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. The exposure time of each image is $\approx 10$ hours. Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles) in a single pointing. East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Analysis}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.  To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission. For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.  We detail our method of continuum subtraction using these data in Section~\ref{sec.cont_sub} below, and follow with a presentation of the resulting surface brightness profiles (Section~\ref{sec.sb}) and EW images (Section~\ref{subsec.ew}).
